Compiling refinement types to dependent types

### 2020-07-07 tex/paper.tex
Remove integers
No need to translate equality in contexts anymore
Also describe in words what \mu_\Gamma does

We take $\lambda C$ \cite{Nederpelt14} enriched with integers and case-splitting as our core dependently typed language.

@@

We start with defining $\mu_\Gamma$:
\begin{equation}
\begin{aligned}
  & \mu_\Gamma(\emptyset)                                       && \triangleq \emptyset                                                     \\
  & \mu_\Gamma(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \nonterm{GC},
                                                                    \gterm x : \mu_\tau(\nonterm{ts})                                       \\
  & \mu_\Gamma(\nonterm G, \nonterm{es}_1 = \nonterm{es}_2)     && \triangleq \nonterm{GC},
                                                                    \mu_\varepsilon(\nonterm{es}_1) \equiv \mu_\varepsilon(\nonterm{es}_2)  \\
\end{aligned}
\end{equation}

>>>>

We take $\lambda C$ \cite{Nederpelt14} enriched with case-splitting as our core dependently typed language.

@@

We start with defining $\mu_\Gamma$,
which merely translates the types of the bindings from the surface language into the core language:
\begin{equation}
\begin{aligned}
  & \mu_\Gamma(\emptyset)                                       && \triangleq \emptyset                                                     \\
  & \mu_\Gamma(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \nonterm{GC},
                                                                    \gterm x : \mu_\tau(\nonterm{ts})                                       \\
\end{aligned}
\end{equation}
